Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
Addding transitions

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}

@@

\subsection{Important Examples}
\raf{Mode, abstain, others?  Mention what is known, especially $\elicpoly($abstain$_{1/2}) \leq \log_2 n$.}

@@

\raf{Transition: wait, what about dimension?}

>>>>

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

We define the elicitation complexities of various classes of loss functions as follows: elic$_\C(\gamma)$ is the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a loss function in the class $\C$.
For example, if $\eliccvx(\gamma) \leq d$, then there is a \emph{convex} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.
Similarly, if $\elicpoly(\gamma) \leq d$, then there is a \emph{polyhedral} loss $L:\reals^d \to \reals^\Y$ that indirectly elicits $\gamma$.

\subsection{Important Examples}
\raf{Mode, abstain, others?  Mention what is known, especially $\elicpoly($abstain$_{1/2}) \leq \log_2 n$.}
Ranking and classification problems are well-known to the field of machine learning.
The most studied classification problem is the elicitation of the mode.
While the mode over $n$ outcomes is elicitable by 0-1 loss, it is known that eliciting the mode by a convex loss is much more difficult.
In fact, the best convex surrogate that can be used to elicit the mode ``embeds'' the reports into $\reals^{n-1}$.
Therefore, we say $\eliccvx($mode$) = n-1$.

A property of interest similar to the mode is the abstain($\alpha$) property, in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
\cite{ramaswamy2018consistent} show that $\elicpoly($abstain$_{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.

@@

\raf{Transition: wait, what about dimension?}
It is well-known that not every property is directly elicitable.
Similarly, we will see shortly that not every elicitable property is embeddable in one dimension.
This leads to what we call embedding complexity: the minimum $d$ such that a property is $d$-embeddable.
In fact, we look at a variety of elicitation complexities restricted to various classes of losses.
In the next section, we show similarities and relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.
